Differentiation By Year

### 2017-11-10 doc/RMD/by-year.Rmd
add seeds to RMD

```{r wmn_amova, cache = TRUE}
bdwmn <- bruvo.dist(wmncc, replen = other(wmncc)$REPLEN)
(wmn.amova <- poppr.amova(wmncc, ~Region/Year, dist = bdwmn))
(wmn.amova.test <- randtest(wmn.amova, nrepet = 999))
make_amova_table(wmn.amova, wmn.amova.test, samples = "Year")
```
```{r, full_amova, cache = TRUE}
bdfull <- bruvo.dist(dat11cc, replen = other(dat11cc)$REPLEN)
(full.amova.2 <- poppr.amova(dat11cc, ~Region/Year, dist = bdfull))
(full.amova.2.test <- randtest(full.amova.2, nrepet = 999)) 
(full.amova.3 <- poppr.amova(dat11cc, ~Region/SourceType/Year, dist = bdfull))
(full.amova.3.test <- randtest(full.amova.3, nrepet = 999))
make_amova_table(full.amova.2, full.amova.2.test, samples = "Year")
make_amova_table(full.amova.3, full.amova.3.test, samples = "Year")
```

>>>>

```{r wmn_amova, cache = TRUE}
bdwmn <- bruvo.dist(wmncc, replen = other(wmncc)$REPLEN)
(wmn.amova <- poppr.amova(wmncc, ~Region/Year, dist = bdwmn))
set.seed(2017-11-10)
(wmn.amova.test <- randtest(wmn.amova, nrepet = 999))
make_amova_table(wmn.amova, wmn.amova.test, samples = "Year")
```
```{r, full_amova, cache = TRUE}
bdfull <- bruvo.dist(dat11cc, replen = other(dat11cc)$REPLEN)
(full.amova.2 <- poppr.amova(dat11cc, ~Region/Year, dist = bdfull))
set.seed(2017-11-10)
(full.amova.2.test <- randtest(full.amova.2, nrepet = 999)) 
(full.amova.3 <- poppr.amova(dat11cc, ~Region/SourceType/Year, dist = bdfull))
set.seed(2017-11-10)
(full.amova.3.test <- randtest(full.amova.3, nrepet = 999))
make_amova_table(full.amova.2, full.amova.2.test, samples = "Year")
make_amova_table(full.amova.3, full.amova.3.test, samples = "Year")
```
